\documentclass[captions=tablesignature]{scrartcl}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{fixltx2e}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{marvosym}
\usepackage{wasysym}
\usepackage{amssymb}
\usepackage{hyperref}
\tolerance=1000
\usepackage{booktabs}
\usepackage[scaled]{beraserif}
\usepackage[scaled]{berasans}
\usepackage[scaled]{beramono}
\usepackage[usenames,dvipsnames]{color}
\usepackage{fancyhdr}
\usepackage{subfig}
\usepackage{listings}
\lstnewenvironment{common-lispcode}
{\lstset{language={HTML},basicstyle={\ttfamily\footnotesize},frame=single,breaklines=true}}
{}
\usepackage{paralist}
\let\itemize\compactitem
\let\description\compactdesc
\let\enumerate\compactenum
\usepackage[letterpaper,includeheadfoot,top=12.5mm,bottom=25mm,left=19mm,right=19mm]{geometry}
\pagestyle{fancy}
\setcounter{secnumdepth}{2}
\author{Percy, Synda, Iya\thanks{programming@nelaonline.org}}
\date{June 2017}
\title{M/s Title Holders Social Event}
\hypersetup{
  pdfkeywords={Zambia, Documentation, FFF branch},
  pdfsubject={This document is a proposal for the M/s Title Holders Social under Events.},
  pdfcreator={}}
\begin{document}

\maketitle
\pagenumbering{roman}
\thispagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\lhead{}
\rhead{}
\chead{}
\lfoot{}
\cfoot{}
\rfoot{}
\begin{abstract}
\vspace{5cm}
{\LARGE{\textbf{Abstract:\\}}}
This document is a proposal for the M/s Title Holders Social under Events.
\end{abstract}
\newpage
\renewcommand{\headrulewidth}{1pt}
\renewcommand{\footrulewidth}{1pt}
\chead{
M/s Title Holders Social Event
}
\lfoot{
Percy, Synda, Iya <programming@nelaonline.org>
}
\rfoot{\thepage}
\setcounter{tocdepth}{2}
\tableofcontents
\newpage
\pagenumbering{arabic}
\section{General Information}
\label{sec-1}
This idea was pitched as part of the Friday Night entertainment /
teaching point of view.  After discussions at TESFest with some of
the title-holders, the number of people ignorant of what that was,
much less the history, pride, and importance of it.  
\subsection{Timing}
\label{sec-1-1}
So we thought a Friday Event would be good to help fill some of
that gap.  Currently the Friday schedule for the Rotunda room has
setup going on through about 5pm, so, depending on the Socials,
this can start either at 6 or at 7, and run through 10:00, with
cleanup and turn-over time so that the RKO Army can start by
11:00.

\subsection{Slack:}
\label{sec-1-2}
\url{http://nela-events.slack.com}

\section{Action Items:}
\label{sec-2}
\subsection{{\bfseries\sffamily TODO} Time-line\hfill{}\textsc{:Everyone:}}
\label{sec-2-1}
Establish the time-line for everything from go/no-go to cleanup.

\subsection{{\bfseries\sffamily TODO} Presenter email\hfill{}\textsc{:Percy:}}
\label{sec-2-2}
Gather a list of all presenters who are title holders, and send
that list to Synda.

\subsection{{\bfseries\sffamily TODO} Volunteer Rewards\hfill{}\textsc{:Percy:}}
\label{sec-2-3}
Send standard volunteer reward chart to Synda.

\subsection{{\bfseries\sffamily TODO} History Project\hfill{}\textsc{:Percy:}}
\label{sec-2-4}
Connect Scott Ericson to Synda.

\subsection{{\bfseries\sffamily TODO} Bootblacks\hfill{}\textsc{:Programming:}}
\label{sec-2-5}
Find out if we want to/are going to move the bootblacks to the
Rotunda for that section of time, and the downstream consequences
of such.

\subsection{{\bfseries\sffamily TODO} Ad rates\hfill{}\textsc{:Percy:}}
\label{sec-2-6}
Get the advertising rates from the Publications team and get them
to Synda so that can be appropriately distributed.

\subsection{{\bfseries\sffamily TODO} Silent Auction\hfill{}\textsc{:Percy:}}
\label{sec-2-7}
Get research librarian to find out any regulations for/around the
possible silent auction.

\subsection{{\bfseries\sffamily TODO} Zambia\hfill{}\textsc{:Percy:}}
\label{sec-2-8}
Make sure Synda and Stephen are set up properly in Zambia.

\subsection{{\bfseries\sffamily TODO} Food\hfill{}\textsc{:Percy:}}
\label{sec-2-9}
There is already the bar set up, get the food prices, and
availability to Synda, as well as the budget for such.

\subsection{{\bfseries\sffamily TODO} EVENTS Team\hfill{}\textsc{:Percy:}}
\label{sec-2-10}
Make sure there is an introduction, and then functional
communications between the EVENTS Team and Synda.

\subsection{{\bfseries\sffamily TODO} Pitch to Stephen\hfill{}\textsc{:Synda:}}
\label{sec-2-11}
See if Stephen is wanting/willing to go along for this ride.

\subsection{{\bfseries\sffamily TODO} MaST\hfill{}\textsc{:Synda:}}
\label{sec-2-12}
Reach to MaSTMass and MaST Rhode Island to see what level of
involvement they would want with this event.

\subsection{{\bfseries\sffamily TODO} Leather Quilt\hfill{}\textsc{:Synda:}}
\label{sec-2-13}
Connect with the current quilt holders, and see about arranging for
it (or a piece of it) to be at the event to show our pride.

\subsection{{\bfseries\sffamily TODO} Presentation of the Colors\hfill{}\textsc{:Synda:}}
\label{sec-2-14}
Research what is needed for this, should this want to be part of
the event.

\subsection{{\bfseries\sffamily TODO} Promotions\hfill{}\textsc{:Synda:}}
\label{sec-2-15}
Build the cards for Publications, and write the content for Social
Media so this can be spread, appropriately.

\subsection{{\bfseries\sffamily TODO} Volunteers\hfill{}\textsc{:Synda:}}
\label{sec-2-16}
Establish a volunteer pool to take care of what is necessary for
the event.  (See also the Volunteer Rewards, above)

\subsection{{\bfseries\sffamily TODO} Other Participants\hfill{}\textsc{:Synda:}}
\label{sec-2-17}
Reach out to other (local?  For some value of local) title-holders
and let them know they are welcome at the event, for some value of
included (to be decided) and compensated with the standard
Volunteer Rewards, if necessary adding setup and cleanup to help
people make their 4 hours.

\section{TIME-LINE}
\label{sec-3}
TBD

\section{People}
\label{sec-4}
TBD

\section{Supplies}
\label{sec-5}
\subsection{BEOs}
\label{sec-5-1}
TBD

\subsection{Us provided}
\label{sec-5-2}
TBD
\end{document}